\subsection*{Chapters in Books}
\begin{enumerate} 
\item \Eagle\ (2019). ``The Growth of the megachurch.'' In Hunt, S.J. (Ed.), \emph{Handbook of Megachurches (pp. 43--67).} Brill.

\item Read, J.G., \& \Eagle \hspace{.01em}  (2014). ``Intersectionality and identity: An exploration of Arab American women.'' In Keister, L.A., \& Sherkat, D. (Eds.), \emph{Religion and inequality in America (pp. 75--96).} Cambridge University Press.

\item \Eagle\ (2013). ``The U.S. mainstream Protestant context.'' In Callahan, S.H. (Ed.), \emph{Religious Leadership: A Reference Handbook.} Sage Publications.
\end{enumerate}

\subsection*{Book Reviews}
\begin{enumerate} 
\item \Eagle\  (2021). ``Beyond Profession: The Next Future of Theological Education by Dan Aleshire." Book review. Accepted for publication in \emph{Practical Theology}.
	
\item \Eagle\  (2018). ``Gay on God’s campus: Mobilizing for LGBT equality at Christian colleges and universities, by Jonathan Coleman." Book review. \emph{Teaching Sociology}. 47(1):67--70. \doi{10.1177/0092055X18814410}

\item \Eagle\ (2017). ``Madness: American Responses to Mental Illness, by Heather Vacek." Book review. \emph{Sociology of Religion}, 78(1): 04--105. \doi{10.1093/socrel/srx005}

\item \Eagle\ (2013). ``Places of Faith: A Road Trip Across America's Religious Landscape, by Chris Scheitle and Roger Finke." Book review.  \emph{Review of Religious Research,} 50(1): 205--206.
\end{enumerate}

\subsection*{Reports and Popular Writing}
\begin{enumerate} 
\item \Eagle\ (2018). ``Theological students and educational Debt: A retrospective study of Duke Divinity School alumni, 2012--2017." Report. Duke Divinity School and the Clergy Health Initiative.

\item \Eagle\ (2016). ``More people, looser ties: Social life in the megachurch.'' \emph{The Christian Century.} 133(4).
\end{enumerate}