\newcommand{\Revision}{\textit{under revision}}
\newcommand{\CS}{*} % corresponding author
\newcommand{\CF}{\textsuperscript{\#}} % co-first author

\section*{Peer-reviewed Publications}
\CS corresponding author, \CF co-first author.

\begin{enumerate}

\item \Eagle, Holleman, A., Olvera, B.B., and Blackwood, E. (2024).``Prevalence of Obesity in Religious Clergy in the United States: A Systematic Review and Meta-Analysis.'' Online ahead of print in \textit{Obesity Reviews}. \doi{10.1111/obr.13741}

\item Gaghan, J., and \Eagle. (2024). RELTRAD2: Refining the State of the Art of Religious Classification by Reconsidering the Categorization of Nondenominational Respondents. Online ahead of print in \textit{Journal for the Scientific Study of Religion}. \doi{10.1111/jssr.12916}

\item Proeschold-Bell, R. J., \Eagle, Tice, L. C., Platt, A., Yao, J., Larkins, J. S., Kim, E. T., \& Rash, J. A. (2024). ``The Selah trial: A preference-based partially randomized waitlist control study of three stress management interventions.''  Forthcoming in \textit{Translational and Behavioral Medicine}.  \doi{10.1093/tbm/ibae017}

\item Holleman, A., Upenieks, L., \& \Eagle. (2024). ``Adverse Childhood Experiences Among Seminarians: Personal Experiences of Trauma and Implications for Pastoral Well-Being and Ministerial Training.'' \textit{Journal of Psychology and Theology}. \doi{10.1177/00916471231206361}

\item Yao J., Steinberg D., Turner L., Cai, G., Cameron J., Hybels C., \Eagle, Milstein G., Rash J., \& Proeschold-Bell, R.J. (2023). ``When shepherds shed: Trajectories of weight, diet and exercise in a holistic health intervention tailored for US Christian clergy.'' \textit{Journal of Religion and Health}. \doi{10.1007/s10943-023-01910-8}

\item Johnston, E.F., \Eagle, \& Headley, J. (2023). ``Pastoring in a Pandemic: Sources and Types of Social Support Used by United Methodist Clergy in the Early Period of the COVID-19 Pandemic.'' \textit{Journal of Psychology and Theology}, 51(4), 459-476. \doi{10.1177/00916471231182737}
	
\item Proeschold-Bell, R.J., \Eagle, Tice, L.C., Yao, J., Rash, J.A., Choi, J.C., Stringfield, B., \& Labrecque, S.A. (2023). ``The Selah Pilot Study of Spiritual, Mindfulness, and Stress Inoculation Practices on Stress-Related Outcomes Among United Methodist Clergy in the United States.'' \textit{Journal of Religion and Health}. \doi{10.1007/s10943-023-01848-x}
	
\item Zwick, H., Asobee, J., Mitton, K.M., Headley, J, \& \Eagle\CS \hspace{0.1em} (2023) ``A Qualitative Study on the Landscape of Burial Workers During an Ebola Outbreak in the Eastern Democratic Republic of the Congo: Community Perceptions, Worker Barriers and Supports Used.''  \textit{Conflict and Health}, 17(25). \doi{10.1186/s13031-023-00521-0}

\item Holleman, A.H. \& \Eagle\hspace{.01em} (2023) ``Is There a Crisis in Clergy Health? Reorienting Research Using a National Sample.'' \textit{Journal for the Scientific Study of Religion}. \doi{10.1111/jssr.12859}

\item Upenieks, L., \& \Eagle\hspace{0.1em} (2023) ``Divine Struggles Among Those Doing God’s Work: A Longitudinal Assessment Predicting Depression and Burnout and the Role of Social Support in United Methodist Clergy.'' \textit{Sociology of Religion}.  \doi{10.1093/socrel/srad014}

\item \Eagle \hspace{.01em} \& Gaghan, J.A. \& Johnston, E.F. (2023). ``Introducing the Seminary to Early Ministry Study.''  \textit{Religious Education}. \doi{10.1080/00344087.2023.2199240}

\item Gaghan, J.A. \& \Eagle \hspace{0.1em} (2023) ``Are Women Elders Paid Less than Men? A Brief Report from the North Carolina Statewide Longitudinal Survey of United Methodist Clergy.'' \textit{Review of Religious Research}. 64:1005--1006. \doi(10.1007/s13644-022-00522-0)
	
\item Biru, B., Yao, J., Plunkett, J., Hybels, C.F., Kim, E. T., \Eagle, Choi, J., \& Proeschold-Bell, R.J. (2022). ``The Gap in Mental Health Service Utilization Among United Methodist Clergy with Anxiety and Depressive Symptoms.'' \emph{Journal of Religion and Health}. \doi{10.1007/s10943-022-01699-y}

\item Johnston, E.F. \& \Eagle  \hspace{.1em} (2022). ``Expanding the Horizontal Call: A Typology of Social Influences on the Call to Ministry.'' \emph{Journal for the Scientific Study of Religion}, 62:68--88.  \doi{10.1111/jssr.12816}

\item \Eagle, \& Mueller, C.W. \hspace{.1em} (2022). ``Reproducing Inequality in a Formally Anti-Racist Organization: The Case of Racialized Career Pathways in the United Methodist Church.'' \emph{American Journal of Sociology}, 127(5): 1507–1550. \doi{10.1086/719391} \vspace{-.5em}
\begin{itemize}
	\item \textit{Winner of the 2023 Best Article Award, Society for the Scientific Study of Religion.}
\end{itemize}
\vspace{-.5em}

\item Johnston, E.F., \Eagle, Corneli, A.L., Perry, B., Proeschold-Bell, R.J.  (2022). ``Seminary Students and Physical Health: Beliefs, Behaviors, and Barriers.'' \emph{Journal of Religion and Health}, 61: 1207--1225. \doi{10.1007/s10943-021-01480-7}

\item Hybels, C.F., Blazer, D.G., \Eagle, \& Proeschold-Bell, R.J. (2022). ``Age Differences in Trajectories of Depressive, Anxiety, and Burnout Symptoms in a Population with a High Likelihood of Persistent Occupational Distress.'' \emph{International Psychogeriatrics}, 34: 21--32. \doi{10.1017/S1041610220001751}

\item Tice, L.C., \Eagle, Rash, J.A., Larkins, J.S., Labrecque, S.M., Platt, A., Yao, J., \& Proeschold-Bell, R.J. (2021). ``The Selah Study Protocol of Three Interventions to Manage Stress Among Clergy: A Preference-Based Randomized Waitlist-Control Trial.''  \emph{Trials}, 22, 892. \doi{10.1186/s13063-021-05845-x}

\item \Eagle, Johnston E.F., Headley, J., \& Holleman, A. (2021). ``The Financial Impacts of COVID-19 on United Methodist Churches in North Carolina: A Qualitative Study of Pastors’ Perspectives and Strategies.'' \emph{Review of Religious Research}. Online ahead of print. \doi{10.1007/s13644-021-00474-x}

\item Proeschold-Bell, R.J., Stringfield, B., Yao, J., Choi, J., \Eagle, Hybels, C., Parnell, H., Keefe, K., \& Shilling, S. (2021). ``Changes in Sabbath-keeping and Mental Health Over Time: Evaluation Findings from the Sabbath Living Study.'' \emph{Journal of Psychology and Theology}. Online ahead of print. \doi{10.1177/00916471211046227}

\item \Eagle, Rash, J., Tice, L., \& Proeschold-Bell, R.J. (2021). ``Evaluation of a Remote, Internet-Delivered Version of the Trier Social Stress Test.'' \emph{International Journal of Psychophysiology}, 165: 137--144. \doi{10.1016/j.ijpsycho.2021.03.009}

\item Liu, X., Whetten, K., Prose, N.S., \Eagle, Parnell, H.E., Amanya, C., Vann, V., Dubie, M.E., Kaza, V.G., Tzudir, S., \& Proeschold-Bell, R.J. (2020). ``Enjoyment and Meaning in Daily Activities Among Caregivers of Orphaned and Separated Children in Four Countries.'' \emph{Children and Youth Services Review}, 116, 105103. \doi{10.1016/j.childyouth.2020.105103}

\item \Eagle, Kinghorn, W.A., Parnell, H.E., Amanya, C., Vann, V., Tzudir, S., Kaza, V.G., Safu, C.T., Whetten, K.A., \& Proeschold-Bell, R.J. (2019). ``Religion and Caregiving for Orphans and Vulnerable Children: A Qualitative Study of Caregivers Across Four Religious Traditions and Five Global Contexts.'' \emph{The Journal of Religion and Health}, 59(3): 1666--1686. \doi{10.1007/s10943-019-00955-y}

\item Lutz, J.R., \& \Eagle\CS\ (2019). ``Social Networks, Support, and Depressive Symptoms: Gender Differences Among Clergy.'' \emph{Socius} 5:2378023119873821. \doi{10.1177/2378023119873821}

\item Kinghorn, W.A., Keyes, C.L., Parnell, H.E., \Eagle, Biru, B.M., Amanya, C., Vann, V., Kaza, V.G., Tzudir, S., Saddo, Y.B., Whetten, K.A., \& Proeschold-Bell, R.J. (2019). ``Putting Virtues in Context: Engaging the VIA Classification of Character Strengths in Caregiving for Orphans and Vulnerable Children Across Cultures.'' \emph{The Journal of Positive Psychology}, 14(6): 845--853. \doi{10.1080/17439760.2019.1579363}

\item Proeschold-Bell, R.J., Molokwu, N.J., Keyes, C.L., Sohail, M.M., \Eagle, Parnell, H.E., Kinghorn, W.A., Amanya, C., Vann, V., Madan, I., Biru, B.M., Lewis, D., Dubie, M.E., \& Whetten, K.A. (2019). ``Caring and Thriving: An International Qualitative Study of Caregivers of Orphaned and Vulnerable Children and Strategies to Sustain Positive Mental Health.'' \emph{Children and Youth Services Review}, 98:143--153. \doi{10.1016/j.childyouth.2018.12.024}

\item Proeschold-Bell, R.J., Steinberg, D.R., Yao, J., \Eagle, Smith, T.W., Cai, G., \& Turner, E.L. (2018). ``Using a Holistic Health Approach to Achieve Long-Term Weight Maintenance: Results from the Spirited Life Intervention.'' \emph{Translational Behavioral Medicine}, 10(1):223-233. \doi{10.1093/tbm/iby117}

\item \Eagle, \& Hybels, C.F. (2018). ``Perceived Social Support, Received Social Support, and Depression Among Clergy.'' \emph{The Journal of Social and Personal Relationships}, 36(7): 2055--2073. \doi{10.1177/0265407518776134}

\item Case, A.D., \Eagle, Yao, J., \& Proeschold-Bell, R.J. (2017). ``Disentangling Race and Socioeconomic Status in Health Disparities Research: An Examination of Black and White Clergy.'' \emph{Journal of Racial and Ethnic Health Disparities}, 5: 1014--1022. \doi{10.1007/s40615-017-0449-7}

\item \Eagle, Keister, L.A., \& Read, J.G. (2017). ``Household Charitable Giving: The Role of Gender, Marital Status, and Religion.'' \emph{Nonprofit and Voluntary Sector Quarterly}. 47(1): 185--205. \doi{10.1177/0899764017734650}

\item Proeschold-Bell, R.J., Turner, E.L., Li, X.F., Yao, J., Bennett, G.G., \& \Eagle, et al. (2017). ``A 2-Year Holistic Health and Stress Intervention: Results of an Intervention in Clergy.'' \emph{American Journal of Preventive Medicine}, 53(3): 290--299. \doi{10.1016/j.amepre.2017.04.009}

\item Smith, T.W., \Eagle\CF, \& Proeschold-Bell, R.J. (2017). ``Prospective Associations Between Depressive Symptoms and the Metabolic Syndrome.'' \emph{Annals of Behavioral Medicine}, 51(4): 610--619. \doi{10.1007/s12160-017-9883-3}

\item \Eagle, Miles, A.J., \& Proeschold-Bell, R.J. (2016). ``The Relationship Between Occupational Relocation and Changes in Mental Health Among Clergy.'' \emph{The Review of Religious Research}, 59(1): 31--45. \doi{10.1007/s13644-016-0263-4}

\item \Eagle \hspace{.01em} (2015). ``The Negative Relationship Between Size and the Probability of Weekly Attendance in Churches in the United States.'' \emph{Socius}, 2: 1--10. \doi{10.1177/2378023115617168}.

\item \Eagle \hspace{.01em} (2015). ``Historicizing the Megachurch.'' \textit{The Journal of Social History}, 48: 589--604. \doi{10.1093/jsh/shu109}

\item \Eagle, \& Proeschold-Bell, R.J. (2015). ``Methodological Considerations in the Use of Name Generators and Interpreters.'' \emph{Social Networks}, 40: 75--78. \doi{10.1016/j.socnet.2014.07.005}

\item Eagle, A.J., \Eagle, Stobbe, T.E., \& Van Kooten, K. (2015). ``Farmland Protection and Agricultural Land Values at the Urban-Rural Fringe.'' \emph{The American Journal of Agricultural Economics}, 97: 282--298. \doi{10.1093/ajae/aau098}

\item Keister, L.A., \& \Eagle \hspace{.01em} (2015). ``Religion and Inequality: The Role of Status Attainment and Social Balance Processes.'' \emph{Social Thought and Research}, 33: 141--174.

\item \Eagle \hspace{.01em} (2012). ``Mega, Medium and Mini: Size and the Socio-Economic Status Composition of American Protestant Congregations.'' \emph{Research in the Sociology of Work}, 23: 281--307. \doi{10.1108/S0277-2833(2012)0000023015}

\item \Eagle \hspace{.01em} (2011). ``The Loosening Bond of Religion on Canadian Society: A Comment on Bibby.'' \emph{Journal for the Scientific Study of Religion}, 50(4): 838--839.
Here is some latex code with references in it. Find the article titles and convert them to title case and return the full latex code back:

\item Read J.G., \& \Eagle \hspace{.01em} (2011). ``Intersecting identities as a source of religious incongruence.''  \emph{Journal for the Scientific Study of Religion}, 50(1): 116--132. \doi{10.1111/j.1468-5906.2010.01555.x}

\item \Eagle \hspace{.01em} (2011). ``Patterns of attendance at religious services in Canada, 1986--2008'' \emph{Journal for the Scientific Study of Religion}, 50(1): 187--200. \doi{10.1111/j.1468-5906.2010.01559.x}

\item \Eagle \hspace{.01em} (2010). ``Pneumatological ecclesiology and same-sex marriage: A non-essentialist ppproach using the work of Eugene Rogers and John Zizioulas.'' \emph{Conrad Grebel Review}, 28(2): 43--68. \href{https://www.davideagle.org/publication/eagle-pneumatological-ecclesiology-samesex-2010/eagle-pneumatological-ecclesiology-samesex-2010.pdf}{PDF}

\item \Eagle\hspace{.01em} (2006). ``Anthony Bartlett's concept of abyssal compassion and the possibility of a truly nonviolent atonement.'' \emph{Conrad Grebel Review}, 26(2): 66--81. \href{https://www.davideagle.org/publication/eagle-anthony-bartlett-concept-2006/eagle-anthony-bartlett-concept-2006.pdf}{PDF}

\end{enumerate}

\subsection*{In Revision/Under Review}
\begin{enumerate}
\item \Eagle, Parker, Ryan, and Asobee, Marc. ``Divergent Views on Depression: Charismatic vs. non- Charismatic Protestant Pastors in the Eastern Democratic Republic of the Congo.'' Under review at \textit{Cambridge Prisms: Global Mental Health.}

\item Rawlings, C.M., \Eagle, \& Johnston, E.F. ``Ideology and Influence:
Sociocognitive Foundations of Belief Change in a Sectarian World.'' Revise and resubmit at the \textit{American Journal of Sociology}.

\item Trexler, E., Eagle, D., Pontzer, H. ``Relationships between oral contraceptive use, physical activity, and chronic inflammation.'' Under review at \textit{PLOS One}.

\item Gaghan, J., \Eagle, and Wilkins-LaFlamme, S. ``The Trump Paradox: 
Unraveling the Ties between Religious Service Attendance, Conservative Protestantism, and Political Affiliation in the Trump Era.'' Under review at \textit{Politics and Religion}.

\end{enumerate}

\subsection*{Chapters in Books}
\begin{enumerate} 
\item \Eagle\ (2019). ``The growth of the megachurch.'' In Hunt, S.J. (Ed.), \emph{Handbook of Megachurches (pp. 43--67).} Brill.

\item Read, J.G., \& \Eagle \hspace{.01em}  (2014). ``Intersectionality and identity: An exploration of Arab American women.'' In Keister, L.A., \& Sherkat, D. (Eds.), \emph{Religion and inequality in America (pp. 75--96).} Cambridge University Press.

\item \Eagle\ (2013). ``The U.S. mainstream Protestant context.'' In Callahan, S.H. (Ed.), \emph{Religious Leadership: A Reference Handbook.} Sage Publications.
\end{enumerate}

\subsection*{Book Reviews}
\begin{enumerate} 
\item \Eagle\  (2022). ``Beyond Profession: The Next Future of Theological Education by Dan Aleshire." Book review.  \emph{Practical Theology}. \doi{https://doi.org/10.1080/1756073X.2022.2113301}
	
\item \Eagle\  (2018). ``Gay on God’s campus: Mobilizing for LGBT equality at Christian colleges and universities, by Jonathan Coleman." Book review. \emph{Teaching Sociology}. 47(1):67--70. \doi{10.1177/0092055X18814410}

\item \Eagle\ (2017). ``Madness: American Responses to Mental Illness, by Heather Vacek." Book review. \emph{Sociology of Religion}, 78(1): 04--105. \doi{10.1093/socrel/srx005}

\item \Eagle\ (2013). ``Places of Faith: A Road Trip Across America's Religious Landscape, by Chris Scheitle and Roger Finke." Book review.  \emph{Review of Religious Research,} 50(1): 205--206. \doi{10.1007/s13644-012-0100-3}
\end{enumerate}

\subsection*{Reports and Popular Writing}
\begin{enumerate} 
\item Roso, J. C., \& \Eagle, D. (2024). Disaffiliation from the United Methodist Church in North Carolina: Challenges and Opportunities. \doi{10.17605/OSF.IO/7ET5R}

\item \Eagle\, \& Mueller, C.W. (2022). ``Unequal careers of Black and White pastors in the United Methodist Church in North and South Carolina.'' Report. Clergy Health Initiative.

\item \Eagle\, Gaghan, J.G. \& Johnston. E.F. (2022). ``Field Education: Student experiences and reflections.'' Report. Seminary to Early Ministry Study.

\item \Eagle\ (2018). ``Theological students and educational debt: A retrospective study of Duke Divinity School alumni, 2012--2017." Report. Duke Divinity School and the Clergy Health Initiative.

\item \Eagle\ (2016). ``More people, looser ties: Social life in the megachurch.'' \emph{The Christian Century.} 133(4).
\end{enumerate}